Verifying Demonstrations

### 2018-11-30 paper/system-model.tex
positions the properties as coming from Delaune, not as traditional for voting; other edits.

\subsection{Assumptions}%
\label{assumptions}

@@

In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest. 
During the protest, the devices might be limited by their batteries in terms of the computations they can perform and only have local connectivity to each other.
No connection to any global network such as the Internet is necessary at that time.  
Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie Internet connections) and are not computationally limited by any battery.
This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.

@@

We draw inspiration from the three traditionally desired properties for verifiability in voting systems:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal%\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

In addition to the verification requirements, we also need to define the 
privacy properties.
In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
\end{description}

%Coercion resistance is not possible to achieve for protests.
Coercion resistance in voting typically relies on physical isolation
(\eg private voting boots), including for digital systems, 
and that is by definition not possible for public events.
For instance, someone could simply physically bring Alice to a protest against her will.
As for receipt freeness, while
desirable \emph{in itself}, it implies a conflict with verifiability in our context:
%appealing at first glance, is not desirable (probably not possible)
%in our context since this will conflict with verifiability:
in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which would make verifiability impossible.

>>>>

\subsection{Model and assumptions}%
\label{assumptions}

@@

In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest. 
During the protest, the devices might be limited by their batteries and computations they can perform and only have local connectivity to each other.
No connection to any global network such as the Internet is necessary at that time.  
Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie Internet connections) and are not computationally limited by any battery.
This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.

@@

We draw inspiration from properties for voting systems as formalized
in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal %\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
privacy properties for voting protocols are given as:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
\end{description}

%Coercion resistance is not possible to achieve for protests.
Coercion resistance in voting typically relies on physical isolation
(\eg private voting booths), including for digital systems, 
and that is by definition not possible for public events.
For instance, someone could simply physically bring Alice to a protest against her will.
As for receipt freeness, while
desirable \emph{in itself}, it implies a conflict with verifiability in our context:
%appealing at first glance, is not desirable (probably not possible)
%in our context since this will conflict with verifiability:
in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which would make verifiability impossible.
